Open quantum systems, i.e., quantum systems that are interacting with an environment, are important for modelling many complex
processes, including the decoherence of quantum computers and many processes in the field of chemical physics.
Most often, these systems cannot be described analytically, but only numerically. Thus, the field of open quantum system
simulation is very important.\\
In many cases, the dynamics of an open quantum system can be described with a Markov approximation, where the state of the environment
is assumed to only depend on the current state of the system. However, in many interesting situations (for example involving short length scales
and high energies), the Markov approximation fails. The environment develops a memory and depends on previous states of the system as well.\\
A popular approach for the simulation of open quantum systems is the Hierarchy Of Pure States (HOPS) \cite{Suess:2014}.
With the HOPS, one can integrate the non-Markovian quantum state diffusion equation and simulate non-Markovian open quantum systems.
Recently it was shown \cite{Gao:2022} that the popular Matrix Product State formalism can be used to derive a Hierarchy Of Matrix Pure States (HOMPS),
which can drastically improve the memory requirements for HOPS. \\
The goal of this thesis is to implement and benchmark both the HOPS method and the HOMPS method in detail. I start by summarizing the theory
which is necessary for understanding both methods in Section \ref{chap:Theory}. This includes the derivation of the HOPS from the non-Markovian
quantum state diffusion equation in Section \ref{sec:HOPS_Derivation} and a brief introduction of Matrix Product States and Matrix Product Operators 
in Section \ref{sec:MPS_Introduction}. 
Next, I explain in detail how the HOPS method can be implemented and test my implementation on the spin-boson model in Section \ref{chap:Implementing_HOPS}.
In Section \ref{chap:Implementing_HOMPS}, I then derive and implement the HOMPS method, and test it on the spin-boson model as well. 
Finally, I give a conclusion and some references on how to further improve the methods in Section \ref{chap:Conclusion}.
\\
My implementation of both HOPS and HOMPS, including the code that was used to generate all plots in this thesis, is openly available
under \cite{Sappler:2023}.


